SMT-Boosted Security Types for Low-Level MPC

### 2025-04-26 esop25/slides.tex
checkpoint

\begin{frame}[fragile]{Modular Typing in Prelude}
  \small{
  \begin{verbatimtab}
SHARED(x) { (m[x]@1 + m[x]@2) }

@@

>>>>

  Applying this rule to, e.g., $\sumthree$ is straightforward given it's syntactic
  form, but applies more generally.

  Yao's Garbled Circuits (YGC) in $\mathbb{F}_{2}$ wire input encoding, using
  $\rx{w}{2}$ as encrypted wire value:
$$
\xassign{\mx{w}{1}}{\mux{\secret{w}}{\neg\flip{w}}{\flip{w}}}{2}
$$
where for all $\be_1,\be_2,\be_3$ (with $\neg$ denoting negation in $\mathbb{F}_2$):
$$
\mux{\be_1}{\be_2}{\be_3} \defeq (\neg\be_1 \ftimes \be_2) \fplus (\be_1 \ftimes \be_3)
$$
and letting this protocol be $\prog$ the following is valid:
\begin{mathpar}
%\toeq{\xassign{\mx{w}{1}}{\OT{\secret{w}}{1}{\neg\flip{w}}{\flip{w}}}{2}}
   \toeq{\prog} \models \mx{w}{1} \eop \neg\sx{w}{2} - \rx{w}{2}
\end{mathpar}
\end{frame}

\begin{frame}{Compositional Typing in Prelude}

The $\metaprot$ language is a \emph{metalanguage} aka metaprogramming
language, where an $\fedprot$ protocol is the result of
computation.
\begin{itemize}
\item Supports compositional verification of larger
  protocols.
\item Confidentiality and integrity properties to be recorded in pre/post
  conditions.
\item Encapsulation and compositional re-use of function property verification.
\end{itemize}

$$
\begin{array}{l}
\ttt{encode}(y,s,r) \{\\
\quad \xassign{\mx{y}{r}}{\mux{\secret{y}}{\neg\flip{y}}{\flip{y}}}{s};\\
% \quad \eqcast{\mx{y}{r}}{\neg\sx{y}{s} \fplus \rx{y}{s}}\\
\}\\
\ttt{postcondition:} ( \mx{y}{r} \eop \neg\sx{y}{s} \fplus \rx{y}{s} )
\end{array}
$$

\begin{frame}[fragile]{Compositional Typing in Prelude}
  \small{
  \begin{verbatimtab}
SHARED(x) { (m[x]@1 + m[x]@2) }

@@

\begin{frame}[fragile]{Compositional Integrity Typing in Prelude}
  \small{
  \begin{verbatimtab}
MACOK(x, i1, i2)
  { m[x++"m"]@i2 ==
    m[x++"k"]@i1 + (m["delta"]@i1 * m[x++"s"]@i2) }

MACed(x) { MACOK(x, 1, 2) AND MACOK(x, 2, 1) }

_sum(z:string, x:string, y:string, i:cid){
    m[z++"s"]@i := (m[x++"s"] + m[y++"s"])@i;
    m[z++"m"]@i := (m[x++"m"] + m[y++"m"])@i;
    m[z++"k"]@i := (m[x++"k"] + m[y++"k"])@i
}

precondition: ( MACed(x) AND MACed(y) )
sum(z:string, x:string, y:string){ _sum(z,x,y,1); _sum(z,x,y,2) }
postcondition: ( MACed(z) )
  \end{verbatimtab}
  }
\end{frame}
